Translation Elicitation: Report

### 2022-03-28 docs/index.Rmd
Add group as a word-level slope

```{r stimuli-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
  select(group, word1, frequency, frequency_zipf, pthn, lv) %>% 
  group_by(group) %>% 
  summarise_at(
    vars(frequency:lv), 
    list(
      median = ~median(., na.rm = TRUE),  
      sd = ~sd(., na.rm = TRUE)
    )
  ) %>%
  gt(rowname_col = "group") %>% 
  tab_header(
    title = md("Table 1"),
    subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
  ) %>% 
  tab_source_note(
    md("*Note*. Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
  ) %>% 
  fmt_number(frequency_median:pthn_sd) %>%
  fmt_percent(matches("lv")) %>% 
  tab_spanner(md("**Freq. (million)**"), c("frequency_median", "frequency_sd")) %>% 
  tab_spanner(md("**Freq. (Zipf)**"), matches("frequency_zipf")) %>% 
  tab_spanner(md("***PTHN***"), matches("pthn")) %>% 
  tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
  cols_label(
    frequency_median = md("Median"),
    frequency_sd = md("*SD*"),
    frequency_zipf_median = md("Median"),
    frequency_zipf_sd = md("*SD*"),
    pthn_median = md("Median"),
    pthn_sd = md("*SD*"),
    lv_median = md("Median"),
    lv_sd = md("*SD*")
  ) %>% 
  summary_rows(
    columns = c(matches("median"), -matches("lv")),
    fns = list(
      Median = "median",
      SD = "sd"
    )
  ) %>% 
  summary_rows(
    columns = matches("lv"),
    fns = list(
      Median = "median",
      SD = "sd"
    ), formatter = fmt_percent
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_stub_grand_summary()
  ) %>% 
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "white"),
    locations = list(
      cells_body(), cells_row_groups(), cells_column_spanners(), 
      cells_stub(), cells_stub_grand_summary(), cells_source_notes(),
      cells_column_labels(), cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(cell_text(align = "left", size = "medium"), cell_borders(sides = "all", color = "white")),
    locations = cells_stub()
  ) %>% 
  tab_style(
    style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
    locations = list(cells_column_spanners(), cells_column_labels())
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:9)
  )

@@

```{r stimuli-frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  distinct(test_language, word1, .keep_all = TRUE) %>% 
  left_join(count(., test_language, name = "n_total")) %>% 
  mutate(test_language = paste0(test_language,  " (N = ", n_total, ")")) %>% 
  ggplot(aes(frequency_zipf, fill = test_language)) +
  facet_wrap(~test_language, ncol = 1) +
  geom_histogram(bins = 25, colour = "white") +
  labs(x = "Lexical frequency (Zipf score)\nExtracted from CLEARPOND database", y = "# trials", fill = "Test language")  +
  scale_y_continuous(breaks = seq(0, 12, 2)) +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

@@

```{r stimuli-pthn, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(count(., test_language, name = "n_total")) %>% 
  mutate(test_language = paste0(test_language,  " (N = ", n_total, ")")) %>% 
  count(test_language, pthn) %>% 
  ggplot(aes(reorder(as.factor(pthn), -n), n, fill = test_language)) +
  facet_wrap(~test_language, ncol = 1) +
  geom_col(position = position_dodge()) +
  labs(x = "# Phonological neighbours with higher lexical frequency\nExtracted from CLEARPOND database", y = "# trials", fill = "Test language") +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

@@

```{r stimuli-similarity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(count(., group, name = "n_total")) %>% 
  mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
  ggplot(aes(group, lv, fill = group, colour = group)) +
  geom_violin() +
  geom_point(shape = 1, stroke = 1, position = position_jitter(width = 0.1), colour = "black", alpha = 0.25) +
  geom_boxplot(colour = "black", fill = "white", width = 0.1, size = 0.75) +
  labs(x = "Group", y = "Phonological Leveshtein distance\n(corrected for string length)", fill = "Test language") +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

@@

# frequency
stimuli %>% 
  mutate(group = case_when(
    group=="ENG-CAT" ~ "cat-ENG",
    group=="ENG-SPA" ~ "spa-ENG",
    group=="SPA-CAT" ~ "cat-SPA",
  )) %>% 
  ggplot(aes(frequency_zipf, fill = group)) + 
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = frequency_zipf_median-frequency_zipf_sd, xmax = frequency_zipf_median+frequency_zipf_sd, 
      ymin = -Inf, ymax = Inf, fill = group
    ), inherit.aes = FALSE, alpha = 0.15
  ) +   
  geom_histogram(bins = 20, colour = "white") +
  geom_vline(
    data = medians, 
    aes(xintercept = frequency_zipf_median, group = group), 
    colour = "black",
    size = 0.5,
    linetype = "dashed"
  ) + 
  geom_text(
    data = medians, 
    aes(
      label = "Median ± SD", 
      x = frequency_zipf_median+1.25,
      y = 13
    ), 
    size = 3
  ) +
  geom_curve(
    data = medians, 
    aes(
      x = frequency_zipf_median+0.85, 
      xend = frequency_zipf_median+0.1,
      y = 12, 
      yend = 11
    ),
    arrow = arrow(length = unit(0.2, "cm")),
    curvature = -0.25,
    colour = "grey30"
  ) +
  labs(
    x = "Lexical frequency (Zipf)", 
    y = "Number of trials", 
    title = "Frequency\n(stimuli translations)\n"
  ) +

  # PTHN
  stimuli %>% 
  count(group, pthn) %>% 
  mutate(group = case_when(
    group=="ENG-CAT" ~ "cat-ENG",
    group=="ENG-SPA" ~ "spa-ENG",
    group=="SPA-CAT" ~ "cat-SPA",
  )) %>% 
  ggplot(aes(pthn, n, fill = group)) + 
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = 0, 
      xmax = pthn_median+pthn_sd, 
      ymin = -Inf, 
      ymax = Inf,
      fill = group
    ), inherit.aes = FALSE, 
    alpha = 0.15
  ) +   
  geom_col(colour = "white") + 
  geom_vline(
    data = medians, aes(xintercept = pthn_median, group = group), 
    colour = "black", size = 0.5, linetype = "dashed"
  ) + 
  labs(
    x = "PTHN", 
    y = "Number of trials", 
    title = "Higher-frequency neighbours\n(stimuli translations)\n"
  ) +

  # Levenshtein
  stimuli %>% 
  mutate(group = case_when(
    group=="ENG-CAT" ~ "cat-ENG",
    group=="ENG-SPA" ~ "spa-ENG",
    group=="SPA-CAT" ~ "cat-SPA",
  )) %>% 
  ggplot(aes(lv, fill = group)) +
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = 0, xmax = lv_median+lv_sd, 
      ymin = -Inf, ymax = Inf, fill = group
    ), inherit.aes = FALSE, alpha = 0.15
  ) +   
  geom_histogram(bins = 20, colour = "white") +
  geom_vline(
    data = medians, aes(xintercept = lv_median, group = group), 
    colour = "black", size = 0.5, linetype = "dashed"
  ) + 
  scale_x_continuous(labels = percent) +
  labs(x = "Levenshtein", y = "Number of trials", title = "Phonological similarity\n(stimuli and stimuli translations)\n") +

  plot_layout(guides = "collect") &
  plot_annotation(tag_levels = "A") &
  scale_fill_manual(values = c("#1A85FF", "#ff2976", "#FFC20A"), na.translate = FALSE) &
  theme(legend.position = "none")

@@

```{r participants_coded, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants_coded <- participants %>% 
  mutate(valid_participant = ifelse(valid_participant, "Valid", "Not valid"))
```

@@

participants_coded %>% 
  count(group, valid_participant) %>% 
  mutate(valid_participant = factor(valid_participant)) %>% 
  ggplot(aes(group, n, fill = valid_participant, order = n)) +
  geom_col() +
  labs(x = "Group", y = "# participants", fill = "Valid?") +
  theme(
    legend.title = element_blank(),
    legend.position = "top",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(linetype = "dotted", colour = "grey")
  )

@@

participants_coded %>% 
  filter(valid_participant=="Valid") %>% 
  select(participant, group, n, n_valid) %>%
  mutate(valid_prop = n_valid/n) %>% 
  ggplot(aes(valid_prop, fill = group, colour = group)) +
  facet_wrap(~group, ncol = 1) +
  geom_histogram() +
  geom_rug() +
  labs(x = "Valid trials (%)", y = "N participants", fill = "Group", colour = "Group") +
  scale_x_continuous(limits = c(0, 1), labels = percent) +
  theme(
    legend.title = element_blank(),
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(linetype = "dotted", colour = "grey")
  )
```

@@

```{r participants_demo, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants_valid <- filter(participants_coded, valid_participant=="Valid")

p_sex <- participants_valid %>% 
  left_join(count(participants_valid, group, name = "n_total")) %>% 
  mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
  ggplot(aes(group, fill = sex)) +
  geom_bar(position = position_fill()) +
  labs(x = "Group", y = "# participants", fill = "Sex") +
  scale_y_continuous(labels = percent) +
  theme(
    legend.position = "top",
    axis.title.x = element_blank()
  )

p_age <- participants_valid %>% 
  left_join(count(participants_valid, group, name = "n_total")) %>% 
  mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
  ggplot(aes(as.factor(age), fill = group, colour = group)) +
  facet_wrap(~group, ncol = 1) +
  geom_bar() +
  labs(x = "Age (years)", y = "% participants", fill = "Group", colour = "Group") +
  theme(
    legend.position = "none"
  )

(p_sex + p_age) &
  plot_layout() &
  plot_annotation(tag_levels = "A") &
  theme(
    legend.title = element_blank(),
    panel.grid.major.y = element_line(linetype = "dotted", colour = "grey")
  )

@@

participants_valid %>% 
  count(group, l2, .drop = FALSE) %>% 
  mutate(
    l2 = case_when(
      l2=="Alemã\u0081n" ~ "German",
      l2=="Francã\u2030s" ~ "French",
      l2=="Cuã\u0081l" ~ "Missing",
      TRUE ~ l2
    ),
  ) %>% 
  left_join(count(participants_valid, group, name = "n_total")) %>% 
  mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
  ggplot(aes(group, n, fill = l2)) +
  facet_wrap(~group, ncol = 1, scales = "free_y") +
  geom_col(position = position_fill()) +
  labs(x = "L2", y = "# participants", fill = "L2") +
  scale_y_continuous(labels = percent) +
  coord_flip() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    strip.text = element_blank(),
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 90),
    axis.title.y = element_blank()
  )

@@

participants_valid %>% 
  select(participant, group, catalan_oral, spanish_oral, catalan_written, spanish_written) %>% 
  mutate_at(vars(catalan_oral, spanish_oral, catalan_written, spanish_written), replace_na, 0) %>% 
  pivot_longer(c(catalan_oral, spanish_oral, catalan_written, spanish_written),
               names_to = "type", values_to = "score") %>% 
  separate(type, c("language", "modality"), sep = "_") %>% 
  mutate_at(vars(language, modality), str_to_sentence) %>%
  left_join(count(participants_valid, group, name = "n_total")) %>% 
  mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
  ggplot(aes(as.integer(score), fill = language)) +
  facet_grid(modality~group) +
  geom_bar(position = position_dodge()) +
  labs(y = "# participants", x = "Self-reported proficiency (0-5)", fill = "Language") +
  theme(
    legend.position = "top",
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

@@

```{r responses_coded, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
responses_coded <- responses %>% 
  # typos are considered correct responses
  mutate_at(vars(group), as.factor) %>% 
  # center predictors
  mutate_at(
    vars(lv_std, pthn_std, frequency_zipf_std),
    function(x) scale(x, center = TRUE, scale = TRUE)[,1]) %>% 
  # impute missing data
  mice(m = 5, print = FALSE, method = "pmm") %>% 
  complete() %>% 
  as_tibble() %>% 
  arrange(group, word)
```

@@

coefs <- fixef(fit_6) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(vars(estimate:q97_5), ~ifelse(variable=="Intercept", inv_logit_scaled(.), ./4))

@@

coefs <- fixef(fit_6) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(vars(estimate:q97_5), ~ifelse(variable=="Intercept", inv_logit_scaled(.), ./4)) %>% 
  group_split(variable) %>% 
  set_names(make_clean_names(map(., "variable"))) %>% 
  map(select, -variable) %>% 
  map(unlist)

>>>>

```{r stimuli-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
  select(
    group,
    word1,
    frequency, 
    frequency_zipf,
    pthn, 
    lv
  ) %>% 
  group_by(group) %>% 
  summarise_at(
    vars(frequency:lv), 
    list(
      median = ~median(., na.rm = TRUE),  
      sd = ~sd(., na.rm = TRUE)
    )
  ) %>%
  gt(rowname_col = "group") %>% 
  tab_header(
    title = md("Table 1"),
    subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
  ) %>% 
  tab_source_note(
    md("*Note*. Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
  ) %>% 
  fmt_number(frequency_median:pthn_sd) %>%
  fmt_percent(matches("lv")) %>% 
  tab_spanner(
    md("**Freq. (million)**"), 
    c("frequency_median", "frequency_sd")
  ) %>% 
  tab_spanner(
    md("**Freq. (Zipf)**"),
    matches("frequency_zipf")) %>% 
  tab_spanner(
    md("***PTHN***"), 
    matches("pthn")) %>% 
  tab_spanner(
    md("**Levenshtein**"),
    matches("lv")) %>% 
  cols_label(
    frequency_median = md("Median"),
    frequency_sd = md("*SD*"),
    frequency_zipf_median = md("Median"),
    frequency_zipf_sd = md("*SD*"),
    pthn_median = md("Median"),
    pthn_sd = md("*SD*"),
    lv_median = md("Median"),
    lv_sd = md("*SD*")
  ) %>% 
  summary_rows(
    columns = c(
      matches("median"), 
      -matches("lv")
    ),
    fns = list(
      Median = "median",
      SD = "sd"
    )
  ) %>% 
  summary_rows(
    columns = matches("lv"),
    fns = list(
      Median = "median",
      SD = "sd"
    ), formatter = fmt_percent
  ) %>% 
  tab_style(
    style = cell_text(
      align = "left",
      weight = "bold", 
      size = "medium"
    ),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(
      align = "left", 
      size = "medium",
      style = "italic"
    ),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(
      align = "left",
      size = "medium"
    ),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = cell_text(
      align = "left",
      size = "medium"
    ),
    locations = cells_stub_grand_summary()
  ) %>% 
  tab_style(
    style = cell_borders(
      sides = c("left", "right"),
      color = "white"
    ),
    locations = list(
      cells_body(), 
      cells_row_groups(), 
      cells_column_spanners(), 
      cells_stub(), 
      cells_stub_grand_summary(),
      cells_source_notes(),
      cells_column_labels(), 
      cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(
      cell_text(
        align = "left", 
        size = "medium"
      ), 
      cell_borders(
        sides = "all", 
        color = "white"
      )
    ),
    locations = cells_stub()
  ) %>% 
  tab_style(
    style = cell_text(
      align = "center",
      size = "medium", 
      weight = "normal", 
      style = "normal"
    ),
    locations = list(
      cells_column_spanners(),
      cells_column_labels()
    )
  ) %>% 
  tab_style(
    style = cell_borders(
      sides = "all",
      color = "white"
    ),
    locations = cells_body(columns = 1:9)
  ) %>% 
  tab_style(
    style = cell_borders(
      sides = "top", 
      color = "white"
    ),
    locations = cells_body(columns = 1:9)
  )

@@

```{r stimuli-frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  distinct(
    test_language,
    word1, 
    .keep_all = TRUE
  ) %>% 
  left_join(
    count(
      ., 
      test_language,
      name = "n_total"
    )
  ) %>% 
  mutate(
    test_language = paste0(
      test_language,  
      " (N = ", n_total, 
      ")"
    )
  ) %>% 
  ggplot() +
  aes(
    frequency_zipf,
    fill = test_language
  ) +
  facet_wrap(
    ~test_language,
    ncol = 1
  ) +
  geom_histogram(
    bins = 25, 
    colour = "white"
  ) +
  labs(
    x = "Lexical frequency (Zipf score)\nExtracted from CLEARPOND database",
    y = "# trials",
    fill = "Test language"
  )  +
  scale_y_continuous(
    breaks = seq(0, 12, 2)
  ) +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(
      colour = "grey", 
      linetype = "dotted"
    )
  )

@@

```{r stimuli-pthn, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(
    count(
      ., 
      test_language, 
      name = "n_total"
    )
  ) %>% 
  mutate(
    test_language = paste0(
      test_language, 
      " (N = ", 
      n_total, 
      ")"
    )
  ) %>% 
  count(
    test_language, 
    pthn
  ) %>% 
  ggplot() +
  aes(
    reorder(as.factor(pthn), -n), 
    n,
    fill = test_language
  ) +
facet_wrap(
  ~test_language,
  ncol = 1
) +
  geom_col(position = position_dodge()) +
  labs(
    x = "# Phonological neighbours with higher lexical frequency\nExtracted from CLEARPOND database",
    y = "# trials",
    fill = "Test language"
  ) +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(
      colour = "grey", 
      linetype = "dotted"
    )
  )

@@

```{r stimuli-similarity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(
    count(
      ., 
      group, 
      name = "n_total"
    )
  ) %>% 
  mutate(
    group = paste0(
      group,  
      " (N = ",
      n_total,
      ")"
    )
  ) %>% 
  ggplot() +
  aes(
    group,
    lv,
    fill = group, 
    colour = group
  ) +
  geom_violin() +
  geom_point(
    shape = 1, 
    stroke = 1, 
    position = position_jitter(width = 0.1),
    colour = "black",
    alpha = 0.25
  ) +
  geom_boxplot(
    colour = "black",
    fill = "white", 
    width = 0.1, 
    size = 0.75
  ) +
  labs(
    x = "Group", 
    y = "Phonological Leveshtein distance\n(corrected for string length)",
    fill = "Test language"
  ) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = scales::percent
  ) +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(
      colour = "grey", 
      linetype = "dotted"
    )
  )

@@

# frequency
stimuli %>% 
  mutate(group = case_when(
    group=="ENG-CAT" ~ "cat-ENG",
    group=="ENG-SPA" ~ "spa-ENG",
    group=="SPA-CAT" ~ "cat-SPA",
  )) %>% 
  ggplot(aes(frequency_zipf, fill = group)) + 
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = frequency_zipf_median-frequency_zipf_sd,
      xmax = frequency_zipf_median+frequency_zipf_sd, 
      ymin = -Inf,
      ymax = Inf, 
      fill = group
    ),
    inherit.aes = FALSE,
    alpha = 0.15
  ) +   
  geom_histogram(
    bins = 20, 
    colour = "white"
  ) +
  geom_vline(
    data = medians, 
    aes(
      xintercept = frequency_zipf_median,
      group = group
    ), 
    colour = "black",
    size = 0.5,
    linetype = "dashed"
  ) + 
  geom_text(
    data = medians, 
    aes(
      label = "Median ± SD", 
      x = frequency_zipf_median+1.25,
      y = 13
    ), 
    size = 3
  ) +
  geom_curve(
    data = medians, 
    aes(
      x = frequency_zipf_median+0.85, 
      xend = frequency_zipf_median+0.1,
      y = 12, 
      yend = 11
    ),
    arrow = arrow(length = unit(0.2, "cm")),
    curvature = -0.25,
    colour = "grey30"
  ) +
  labs(
    x = "Lexical frequency (Zipf)", 
    y = "Number of trials", 
    title = "Frequency\n(stimuli translations)\n"
  ) +

  # PTHN
  stimuli %>% 
  count(
    group, 
    pthn
  ) %>% 
  mutate(
    group = case_when(
      group=="ENG-CAT" ~ "cat-ENG",
      group=="ENG-SPA" ~ "spa-ENG",
      group=="SPA-CAT" ~ "cat-SPA",
    )) %>% 
  ggplot() + 
  aes(
    pthn, 
    n,
    fill = group
  ) +
  facet_wrap(
    ~group,
    ncol = 1
  ) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = 0, 
      xmax = pthn_median+pthn_sd, 
      ymin = -Inf, 
      ymax = Inf,
      fill = group
    ),
    inherit.aes = FALSE, 
    alpha = 0.15
  ) +   
  geom_col(colour = "white") + 
  geom_vline(
    data = medians, 
    aes(
      xintercept = pthn_median, 
      group = group
    ), 
    colour = "black", 
    size = 0.5,
    linetype = "dashed"
  ) + 
  labs(
    x = "PTHN", 
    y = "Number of trials", 
    title = "Higher-frequency neighbours\n(stimuli translations)\n"
  ) +

  # Levenshtein
  stimuli %>% 
  mutate(
    group = case_when(
      group=="ENG-CAT" ~ "cat-ENG",
      group=="ENG-SPA" ~ "spa-ENG",
      group=="SPA-CAT" ~ "cat-SPA",
    )) %>% 
  ggplot() +
  aes(
    lv, 
    fill = group
  ) +
  facet_wrap(
    ~group,
    ncol = 1
  ) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = 0,
      xmax = lv_median+lv_sd, 
      ymin = -Inf,
      ymax = Inf, 
      fill = group
    ), 
    inherit.aes = FALSE, 
    alpha = 0.15
  ) +   
  geom_histogram(
    bins = 20,
    colour = "white"
  ) +
  geom_vline(
    data = medians, 
    aes(
      xintercept = lv_median,
      group = group
    ), 
    colour = "black", 
    size = 0.5, 
    linetype = "dashed"
  ) + 
  scale_x_continuous(labels = percent) +
  labs(
    x = "Levenshtein", 
    y = "Number of trials",
    title = "Phonological similarity\n(stimuli and stimuli translations)\n"
  ) +

  plot_layout(
    guides = "collect"
  ) &
  plot_annotation(
    tag_levels = "A"
  ) &
  scale_fill_manual(
    values = c(
      "#1A85FF",
      "#ff2976",
      "#FFC20A"
    ),
    na.translate = FALSE
  ) &
  theme(
    legend.position = "none"
  )

@@

```{r participants_coded, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants_coded <- participants %>% 
  mutate(
    valid_participant = ifelse(
      valid_participant, 
      "Valid", 
      "Not valid"
    )
  )
```

@@

participants_coded %>% 
  count(
    group,
    valid_participant
  ) %>% 
  mutate(
    valid_participant = factor(valid_participant)
  ) %>% 
  ggplot() +
  aes(
    group, 
    n, 
    fill = valid_participant, 
    order = n
  ) +
  geom_col() +
  labs(
    x = "Group",
    y = "# participants", 
    fill = "Valid?"
  ) +
  theme(
    legend.title = element_blank(),
    legend.position = "top",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(
      linetype = "dotted", 
      colour = "grey"
    )
  )

@@

participants_coded %>% 
  filter(
    valid_participant=="Valid"
  ) %>% 
  select(
    participant, 
    group, 
    n, 
    n_valid
  ) %>%
  mutate(
    valid_prop = n_valid/n
  ) %>% 
  ggplot() +
  aes(
    valid_prop,
    fill = group,
    colour = group
  ) +
  facet_wrap(
    ~group, 
    ncol = 1
  ) +
  geom_histogram() +
  geom_rug() +
  labs(
    x = "Valid trials (%)", 
    y = "N participants",
    fill = "Group", 
    colour = "Group"
  ) +
  scale_x_continuous(
    limits = c(0, 1), 
    labels = percent
  ) +
  theme(
    legend.title = element_blank(),
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(
      linetype = "dotted", 
      colour = "grey"
    )
  )
```

@@

```{r participants_demo, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
participants_valid <- participants_coded %>% 
  filter(valid_participant=="Valid")

p_sex <- participants_valid %>% 
  left_join(
    count(
      participants_valid, 
      group, 
      name = "n_total"
    )
  ) %>% 
  mutate(
    group = paste0(group,  "\n(N = ", n_total, ")")
  ) %>% 
  ggplot() +
  aes(
    group, 
    fill = sex
  ) +
  geom_bar(position = position_fill()) +
  labs(
    x = "Group",
    y = "# participants",
    fill = "Sex"
  ) +
  scale_y_continuous(labels = percent) +
  theme(
    legend.position = "top",
    axis.title.x = element_blank()
  )

p_age <- participants_valid %>% 
  left_join(
    count(
      participants_valid, 
      group, 
      name = "n_total"
    )
  ) %>% 
  mutate(
    group = paste0(group,  " (N = ", n_total, ")")
  ) %>% 
  ggplot() +
  aes(
    as.factor(age), 
    fill = group, 
    colour = group
  ) +
  facet_wrap(
    ~group,
    ncol = 1
  ) +
  geom_bar() +
  labs(
    x = "Age (years)",
    y = "% participants", 
    fill = "Group", 
    colour = "Group"
  ) +
  theme(
    legend.position = "none"
  )

(p_sex + p_age) &
  plot_layout() &
  plot_annotation(tag_levels = "A") &
  theme(
    legend.title = element_blank(),
    panel.grid.major.y = element_line(
      linetype = "dotted", 
      colour = "grey"
    )
  )

@@

participants_valid %>% 
  count(
    group,
    l2, 
    .drop = FALSE
  ) %>% 
  mutate(
    l2 = case_when(
      l2=="Alemã\u0081n" ~ "German",
      l2=="Francã\u2030s" ~ "French",
      l2=="Cuã\u0081l" ~ "Missing",
      TRUE ~ l2
    ),
  ) %>% 
  left_join(
    count(
      participants_valid,
      group, 
      name = "n_total"
    )
  ) %>% 
  mutate(
    group = paste0(group,  "\n(N = ", n_total, ")")
  ) %>% 
  ggplot() +
  aes(
    group,
    n, 
    fill = l2
  ) +
  facet_wrap(
    ~group,
    ncol = 1, 
    scales = "free_y"
  ) +
  geom_col(position = position_fill()) +
  labs(
    x = "L2",
    y = "# participants",
    fill = "L2"
  ) +
  scale_y_continuous(
    labels = percent
  ) +
  coord_flip() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    strip.text = element_blank(),
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 90),
    axis.title.y = element_blank()
  )

@@

participants_valid %>% 
  select(
    participant,
    group, 
    catalan_oral,
    spanish_oral, 
    catalan_written,
    spanish_written
  ) %>% 
  mutate_at(
    vars(
      catalan_oral,
      spanish_oral,
      catalan_written, 
      spanish_written
    ),
    replace_na, 
    0
  ) %>% 
  pivot_longer(
    c(
      catalan_oral, 
      spanish_oral,
      catalan_written,
      spanish_written
    ),
    names_to = "type", 
    values_to = "score"
  ) %>% 
  separate(
    type, 
    c("language", "modality"),
    sep = "_"
  ) %>% 
  mutate_at(
    vars(language, modality), 
    str_to_sentence
  ) %>%
  left_join(
    count(
      participants_valid,
      group,
      name = "n_total"
    )
  ) %>% 
  mutate(
    group = paste0(group,  " (N = ", n_total, ")")
  ) %>% 
  ggplot() +
  aes(
    as.integer(score), 
    fill = language
  ) +
  facet_grid(modality~group) +
  geom_bar(
    position = position_dodge()
  ) +
  labs(
    y = "# participants",
    x = "Self-reported proficiency (0-5)",
    fill = "Language"
  ) +
  theme(
    legend.position = "top",
    panel.grid.major.y = element_line(
      colour = "grey",
      linetype = "dotted"
    )
  )

@@

```{r responses_coded, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
responses_coded <- responses %>% 
  # typos are considered correct responses
  mutate_at(
    vars(group), 
    as.factor
  ) %>% 
  # center predictors
  mutate_at(
    vars(
      lv_std, 
      pthn_std,
      frequency_zipf_std
    ),
    function(x) {
      scale(
        x, 
        center = TRUE, 
        scale = TRUE
      )[,1]
    }
  ) %>% 
  # impute missing data
  mice(
    m = 5, 
    print = FALSE,
    method = "pmm"
  ) %>% 
  complete() %>% 
  as_tibble() %>% 
  arrange(
    group,
    word
  )
```

@@

coefs <- fixef(fit_6) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(
    vars(estimate:q97_5), 
    ~ifelse(
      variable=="Intercept",
      inv_logit_scaled(.),
      ./4
    )
  )

@@

coefs <- fixef(fit_6) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(
    vars(estimate:q97_5), 
    ~ifelse(
      variable=="Intercept", 
      inv_logit_scaled(.), 
      ./4
    )
  ) %>% 
  group_split(variable) %>% 
  set_names(make_clean_names(map(., "variable"))) %>% 
  map(select, -variable) %>% 
  map(unlist)

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:groupENGvs.SPA" = "Levenshtein \u00d7 Group 1",
  "lv_std:groupENGMCATvs.ENGMSPA" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "groupENGvs.SPA" =  "Group 1\n[*-ENG vs. cat-SPA]",
  "groupENGMCATvs.ENGMSPA" = "Group 2\n[cat-ENG vs. spa-ENG]"
)
